Figures

### 2018-11-15 figures/02_hierarchical_demo.Rmd
rm points, recolor chloropleth

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
library(kableExtra)
library(dplyr)
library(tidyr)
library(magrittr)

library(LAGOSNE)
library(LAGOSextra)
library(sf)
library(ggplot2)
library(cowplot)

@@

@@

```{r 02_hierarchical_demo, fig.height=3, echo=FALSE}
lg <- lagosne_load("1.087.1")

@@

plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    ylim(0, 300),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank()), 
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```

>>>>

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
library(dplyr)
library(LAGOSextra)
library(sf)
library(ggplot2)
library(cowplot)
library(classInt)

@@

n_cat  <- 6
colors <- c("#FFFFFF", viridisLite::viridis(n_cat - 1))
hu4    <- mutate(hu4, 
                 n_cat = cut(hu4$n, breaks = classInt::classIntervals(hu4$n, n = n_cat)$brks))
hu4 <- dplyr::filter(hu4, !is.na(n_cat))

@@

```{r 02_hierarchical_demo, fig.height=3, echo=FALSE}
library(tidyr)
library(LAGOSNE)

lg <- lagosne_load("1.087.1")

@@

plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)), 
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```
